Automated Program Verification and Synthesis of Embedded \& Cyber-physical Systems: Advances and Challenges

### 2017-08-03 paper.tex
reviewed section 8
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

This paper presented the main challenges related to the verification of design correctness, in embedded systems, and also raised some important side considerations about synthesis. In particular, it emphasizes that stringent constraints imposed by the underlying hardware ({\it e.g.}, real-time, memory allocation, interrupts, and concurrency), along with system behavior models, must be considered during verification and synthesis. Additionally, there is little evidence that model checking embedded software using \textit{k}-induction (and invariants), which
extends BMC-based approaches from falsification to verification, can be applied to formally verify correctness and timeliness of embedded systems.

Given that software complexity has significantly increased in embedded products, there are still some (recent) advances to stress and exhaustively cover the system state space, in order to verify low-level properties that have to meet the application's deadline, access memory regions, handle concurrency, and control hardware registers. There is a trend towards incorporating knowledge about the system to be verified, which may take software verification and synthesis one step further, where not only code correctness will be addressed, but also full system reliability. In addition, it seems interesting to provide behavioral models when new application interfaces or programming language features are used, in order to extend capabilities of current verification tools, without changing the core BMC module. Finally, there are some bottlenecks in software verification that are possible to be handled with machine learning, given some initial studies carried out in the current literature, which may represent another step towards a unified and complete approach that combines code verification, behavior correctness, environment adaptation, and system evolution.

As future work, the main goal of this research is to extend BMC as a design, verification, and synthesis tool for achieving correct-by-construction embedded system implementations. Special attention will be given to cyber-physical systems and modern micro-grids, considering small-scale versions of a distributed system, so that reliability and other system-level properties ({\it e.g.}, carbon emission reduction in smart cities) are amenable to automated verification, probably through behavior models. Additionally, ML techniques will be incorporated to BMC frameworks, in order to provide flexibility and specific-problem tuning.

>>>>

This paper presented the main challenges related to the verification of design correctness, in ECPS, and also raised some important side considerations about synthesis. In particular, it emphasizes that stringent constraints imposed by the underlying hardware ({\it e.g.}, real-time, memory allocation, interrupts, and concurrency), along with system behavior models, must be considered during verification and synthesis. Additionally, there is little evidence that model checking ECPS using \textit{k}-induction (and invariants), which extends BMC-based approaches from falsification to verification, can be applied to formally verify correctness and timeliness of ECPS.

Given that software complexity has significantly increased in ECPS, there are still some (recent) advances to stress and exhaustively cover the system state space, in order to verify low-level properties that have to meet the application's deadline, access memory regions, handle concurrency, and control hardware registers. There is a trend towards incorporating knowledge about the system to be verified, which may take software verification and synthesis one step further, where not only code correctness will be addressed, but also full system reliability. In addition, it seems interesting to provide behavioral models when new application interfaces or programming language features are used, in order to extend capabilities of current verification tools, without changing the core BMC module. Finally, there are some bottlenecks in software verification that are possible to be handled with machine learning, given some initial studies carried out in the current literature, which may represent another step towards a unified and complete approach that combines code verification, behavior correctness, environment adaptation, and system evolution.

As future work, the main goal of this research is to extend BMC as a design, verification, and synthesis tool for achieving correct-by-construction ECPS implementations. Special attention will be given to modern micro-grids, considering small-scale versions of a distributed system, so that reliability and other system-level properties ({\it e.g.}, carbon emission reduction in smart cities) are amenable to automated verification and synthesis, probably through behavior models. Additionally, ML techniques will be incorporated to BMC frameworks, in order to provide flexibility and specific-problem tuning.
